Networked Character Devices

### 2011-12-10 report/presentation.tex
presentation: client/server swap (typo)
Related Work slide

\begin{frame}{Related Work}
  \begin{itemize}
    \item nfs
    \item nbd
    \item CUSE
    \item USB/IP Project
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item<1-> The server side resides entirely in a single kernel module
    \item<2-> The client side is a standard userspace server
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Related Work}
  \begin{itemize}
    \item NFS
    \begin{itemize}
      \item Access to remote file system, but no devices
      \item Safe access
      \item http://nfs.sourceforge.net/
    \end{itemize}
    \item NBD
    \begin{itemize}
      \item Network Block Device- Introduced in Linux kernel 2.1.101
      \item Works with any file system but no exclusive access 
      \item http://nbd.sourceforge.net/
    \end{itemize}
    \item CUSE
    \begin{itemize}
      \item Character Device in User Space (extension of FUSE)- Linux kernel 2.6.31
      \item http://lwn.net/Articles/308445/
    \end{itemize}
    \item USB/IP Project
    \begin{itemize}
      \item USB device sharing over IP
      \item http://usbip.sourceforge.net/
    \end{itemize}

  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item<1-> The client side resides entirely in a single kernel module
    \item<2-> The server side is a standard userspace daemon
  \end{itemize}
\end{frame}
